Achieving maximum possible precision on stellar radial-velocity measurements in multi-epoch spectroscopy

### 2017-12-01 paper/paper.tex
crlb text

\newcommand{\unit}[1]{\mathrm{#1}}
\newcommand{\km}{\unit{km}}
\newcommand{\m}{\unit{m}}
\newcommand{\s}{\unit{s}}
\newcommand{\kms}{\km\,\s^{-1}}
\newcommand{\ms}{\m\,\s^{-1}}
\newcommand\todo[1]{\textcolor{red}{#1}}  % gotta have \usepackage{xcolor} in main doc or this won't work
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\HARPS}{\project{\acronym{HARPS}}}
\newcommand{\RV}{\acronym{RV}}
\newcommand{\CRLB}{\acronym{CRLB}}

@@

@@

\begin{itemize}
\item what is the Cramer-Rao bound on a spectrum?
\item Butler equation
\item Bouchy equation
\item Figueira (or Lovis \& Fischer) equation
\end{itemize}

>>>>

\newcommand{\unit}[1]{\mathrm{#1}}
\newcommand{\km}{\unit{km}}
\newcommand{\m}{\unit{m}}
\newcommand{\s}{\unit{s}}
\newcommand{\kms}{\km\,\s^{-1}}
\newcommand{\ms}{\m\,\s^{-1}}
\newcommand\todo[1]{\textcolor{red}{#1}}  % gotta have \usepackage{xcolor} in main doc or this won't work
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\HARPS}{\project{\acronym{HARPS}}}
\newcommand{\RV}{\acronym{RV}}
\newcommand{\CRLB}{\acronym{CRLB}}
\newcommand{\EPRV}{\acronym{EPRV}}

@@

Given finite, noisy data, there are limits coming from information
theory on how well any parameter of interest can be measured.
The most straightforward bound is the Cram\'er--Rao Lower Bound (\CRLB) on the
variance of any unbiased frequentist estimator.
Estimators can only beat this bound by taking on bias.

The \CRLB\ is related to the Fisher Information that is frequently
used in cosmological experiment forecasts.

This bound is strong, but it cannot be calculated \emph{objectively};
any description of the information in a data set requires
subjective decisions (that is, debatable decisions), which are inputs
to a model for the generation of the data.
In particular, information-theory bounds require a model for the
probability of the data given the parameter of interest; that is, they
require a likelihood function.
(Side note: Bayesians need a likelihood function for inference, and
frequentists need a likelihood function for analyzing their estimators.
The likelihood function is central to all statistical methods.)

In the case of \EPRV, this says that it is impossible to compute the
CRLB without making assumptions about the stellar spectrum (the
latent, unobserved, \emph{true} spectrum that could only be observed
with arbitrarily good data) and the noise processes that distort the
spectrum in any finite, noisy observation.

These noise processes necessarily must include any beliefs about
unsubtracted telluric absorptions or emissions, and time variability
of the star itself, not to mention photon and spectrograph read and
extraction noise.

The issue with

@@

\begin{itemize}
\item what is the Cramer-Rao bound on a spectrum? See notes in Hogg's red book for 2017-12-01.
\item Butler equation
\item Bouchy equation
\item Figueira (or Lovis \& Fischer) equation
\end{itemize}
